%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% -------------- README --------------
% Visit https://github.com/vgnshiyer/ASU-sparkysundevil-resume-template for comprehensive documenation.

% -------------- Resume ---------------
\documentclass{resume}

\begin{document}

% --------- Contact Information -----------
\introduction[
    fullname={MUNAGALA KRISHNA SAI},
    email={munagalakrishnasai1@gmail.com},
    phone={+91 8919593028},
    linkedin={linkedin.com/in/munagalakrishnasai1}
]

% --------- Summary -----------
\summary{Full-stack developer over 1.5 years of experience at EXL Digital in Product Development, specializing in .NET, Python and Angular. Skilled in both 
front-end and back-end development, with a strong focus on building and maintaining web applications}

\begin{educationSection}{Education}
    \educationItem[
        university={IIIT Delhi},
        graduation={Jun 2021 – May 2023},
        grade={8.2 CGPA},
        program={M.Tech, Computer Science Engineering},
        coursework={ML, DeepLearning, Algorithms},
    ] \\
     \educationItem[
        university={SRM Institute Of Science \& Technology},
        graduation={Jun 2017 – May 2021},
        grade={9.1 CGPA},
        program={B.Tech, Computer Science Engineering},
        coursework={Data Structures, Algorithms, Python, CPP, Dotnet Core}
    ]
\end{educationSection}


% --------- Skills -----------
\begin{skillsSection}{Technical Skills}
    \skillItem[
        category={Languages},
        skills={C, C++, Python, Java, C\#}
    ] \\
    \skillItem[
        category={Frameworks \& Tools},
        skills={Angular, Dotnet, Postman, Git, CI/CD pipelines, AWS, Docker}
    ] \\
    \skillItem[
        category={Databases},
        skills={SQL, PostgreSQL, MongoDB, Database Management Using SSMS}
    ]
\end{skillsSection}

% --------- Experience -----------
\begin{experienceSection}{Work Experience}
    \experienceItem[
        company={EXL Digital},
        location={Noida Sec-144},
        position={FullStack Developer},
        duration={Aug 2023 – Present}
    ]
    \begin{itemize}
        \itemsep -6pt {}
         \item Developed and deployed 100+ high-performance APIs using .NET and Python for diverse multitenant applications, optimizing scalability and enhancing the overall application efficiency.
      
        \item Engineered a robust data processing API pipeline, efficiently managing 20+ complex Formio JSON structures, significantly improving overall operational efficiency.
        \item Developed a fully responsive and user-friendly website using Angular, ensuring seamless performance across all devices, leading to a 20\% increase in user satisfaction.
        \item Implemented Single Sign-On (SSO) with API authorization leveraging Bearer tokens, alongside developing an OTP-based email login system seamlessly integrated with Microsoft Graph API to enhance security and user authentication processes.
        \item Designed and implemented an AWS Lambda function to automate a cron job that processed Excel files from S3, converted them to JSON, and saved the JSON back to S3. Stored the file location and data in a database for efficient retrieval and management.
        \item Pioneered the automation of the onboarding process through the strategic design and implementation of a Camunda workflow, significantly reducing complexity and enhancing efficiency. Streamlined the process by making the flow and code dynamic, enabling scalability, adaptability, and improved maintainability for future requirements.
       
    \end{itemize}

    \experienceItem[
        company={Nokia},
        location={Chennai},
        position={Web Developer Intern},
        duration={Jun 2018 – Jul 2018}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Enhanced the existing UI by optimizing design elements and improving user workflows, resulting in a more intuitive and visually appealing interface.

    \end{itemize}

\end{experienceSection}

% --------- Projects -----------
\begin{experienceSection}{projects}
    \projectItem[
        title={ Ultrasound Placental Image Analysis Using Deep Learning},
        duration={Aug 2022 – March 2020},
        keyHighlight=Collaborated with a team of five to modify CNN models such as VGG16 and ResNet\, fine-tuning them to achieve optimal performance on our dataset.
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Modified and implemented multiple machine learning ML and neural network models to classify the trimesters.
        \item Performed data augmentation to increase the dataset size by 30\%, enhancing model training and improving performance; findings were documented and published in a research paper.
        
    \end{itemize}

    \projectItem[
        title=DLPM Data Lead Payable Management,
        duration={Feb 2024 – Nov 2024},
        keyHighlight=Awarded the Best Team Contributor Award for exceptional collaboration and significant contributions to project success.
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item  Streamlined accounts receivable processes by deploying an automated tool to classify invoices into PO and Non-PO categories.
        \item Designed and deployed a machine learning-based classification model to categorize invoices into PO and Non-PO types with nearly 95\% accuracy. Automated the extraction and converted invoice data into JSON format for structured storage in a database, enabling seamless integration with downstream processes and enhanced data accessibility.
        \item Enabled automated 2-way or 3-way matching for PO-based orders by integrating email-based invoice retrieval, reducing manual intervention and human errors. Optimized non-PO invoice workflows for enhanced accuracy and faster processing. Improved processing efficiency by automating invoice matching with Purchase Orders (POs) and Goods Receipt Notes (GRNs), reducing invoice processing time by 30\% and minimizing errors by 25\%.
        \item Improved compliance with procurement policies and reduced payment cycle times through automated checks and validations. Facilitated seamless integration with existing ERP systems, ensuring scalability and compatibility across multiple processes.
        % \item Developed multiple Rest and GraphQL API's
        % \item Designed and integrated JSON Web Token (JWT)-based authentication and authorization mechanisms, ensuring secure and efficient access control across the application.
    \end{itemize}

    % \projectItem[
    %     title = Cryptocurrency Price Prediction
    %     duration={June 2021 Nov 2021},
    %     keyHighlight=Leveraged historical data to design and implement a predictive model for cryptocurrency prices
    % ]
    % \begin{itemize}
    %     \vspace{-0.5em}
    %     \itemsep -6pt {}
    %     \item Large Language Models LLMs) demonstrated a 10% increase in accuracy compared to other regression models when applied to large datasets
    % \end{itemize}
\end{experienceSection}



% % --------- Other work experience -----------
% \begin{experienceSection}{Other work experience}
%     \experienceItem[
%         company={Arizona State University},
%         location={Tempe, AZ},
%         position={Tutor (10 hours/week)},
%         duration={Aug 2018 – May 2019}
%     ]
%     \begin{itemize}
%         \vspace{-0.2em}
%         \itemsep -6pt {}
%         \item Tutored 10-15 undergraduate engineering students per week in MATLAB programming and math coursework
%     \end{itemize}

%     \experienceItem[
%         company={Kohl's},
%         location={Gilbert, AZ},
%         position={Sales Associate, Jewelry Department (16-24 hours/week)},
%         duration={Aug 2017 – Dec 2017}
%     ]
%     \begin{itemize}
%         \vspace{-0.2em}
%         \itemsep -6pt {}
%         \item Achieved \#2 highest selling associate within one month of hire date
%     \end{itemize}
% \end{experienceSection}

% --------- Activities -----------
% \begin{experienceSection}{Activities}
%     \projectItem[
%         title={ASU Society of Women Engineers (SWE)},
%         keyHighlight={Multiple leadership roles, including vice-president and industry relations chair (300 members{,} \$75k annual budget)},
%         duration={Aug 2017 – Present}
%     ]
%     \begin{itemize}
%         \vspace{-0.5em}
%         \itemsep -6pt {}
%         \item Tutored 10-15 undergraduate engineering students per week in MATLAB programming and math coursework
%         \item Organized 2018 annual conference participation, including 8 student poster submissions
%     \end{itemize}
% \end{experienceSection}

\end{document}
