\documentclass{resume}

\begin{document}
\introduction[
    fullname={MUNAGALA susmitha sen},
    email={munagalakrishnasai1@gmail.com},
    phone={+91 8919593028},
    linkedin={linkedin.com/in/munagalakrishnasai1}
]

% --------- Summary -----------
\summary{Experienced Full-Stack Developer with expertise in .NET and Angular, passionate about building scalable and efficient applications.  Strong problem-solving skills and a proven ability to deliver high-quality software solutions within tight deadlines.}

\begin{educationSection}{Education}
    \educationItem[
        university={IIT Delhi},
        graduation={Jun 2021 -- May 2023},
        grade={8.2 CGPA},
        program={M.Tech, Computer Science Engineering},
        coursework={ML, Deep Learning, Algorithms, Data Structures}
    ] \\ 
    \educationItem[
        university={SRM Institute Of Science \& Technology},
        graduation={Jun 2017 -- May 2021},
        grade={9.1 CGPA},
        program={B.Tech, Computer Science Engineering},
        coursework={Data Structures, Algorithms, Python, C++, Dotnet Core, Database Management}
    ]
\end{educationSection}


% --------- Skills -----------
\begin{skillsSection}{Technical Skills}
    \skillItem[
        category={Languages},
        skills={C, C++, Python, Java, C\#}
    ] \\ 
    \skillItem[
        category={Frameworks \& Tools},
        skills={Angular, .NET, Postman, Git, Docker, Kubernetes, CI/CD pipelines, AWS}
    ] \\ 
    \skillItem[
        category={Databases},
        skills={SQL, PostgreSQL, MongoDB, Database Management Using SSMS}
    ]
\end{skillsSection}

% --------- Experience -----------
\begin{experienceSection}{Work Experience}
    \experienceItem[
        company={EXL Digital},
        location={Noida Sec-144},
        position={FullStack Developer},
        duration={Aug 2023 -- Present}
    ]
    \begin{itemize}
        \itemsep -6pt
        \item Developed and deployed 100+ high-performance APIs using .NET and Python for diverse multitenant applications, optimizing scalability and enhancing overall application efficiency.  Demonstrating strong coding skills and API design patterns.
        \item Engineered a robust data processing API pipeline, efficiently managing 20+ complex Formio JSON structures, significantly improving overall operational efficiency.  Used modern software development practices.
        \item Developed a fully responsive and user-friendly website using Angular, ensuring seamless performance across all devices, leading to a 20\% increase in user satisfaction.  Ensuring high quality and positive user experience.
        \item Implemented Single Sign-On (SSO) with API authorization leveraging Bearer tokens, alongside developing an OTP-based email login system seamlessly integrated with Microsoft Graph API to enhance security and user authentication processes.  Addressing critical security challenges.
        \item Designed and implemented an AWS Lambda function to automate a cron job that processed Excel files from S3, converted them to JSON, and saved the JSON back to S3.  Significant automation contributions.
        \item Pioneered the automation of the onboarding process through the strategic design and implementation of a Camunda workflow, significantly reducing complexity and enhancing efficiency.  Improving operational efficiency and reducing cost.
    \end{itemize}
    \experienceItem[
        company={Nokia},
        location={Chennai},
        position={Web Developer Intern},
        duration={Jun 2018 -- Jul 2018}
    ]
    \begin{itemize}
        \itemsep -6pt
        \item Enhanced the existing UI by optimizing design elements and improving user workflows, resulting in a more intuitive and visually appealing interface.  Improving user experience and implementing best practices.
        \item Worked within a team environment, collaborating effectively with colleagues to deliver projects on time and within budget.
    \end{itemize}
\end{experienceSection}

% --------- Projects -----------

\begin{experienceSection}{Projects}
    \projectItem[
        title={Ultrasound Placental Image Analysis Using Deep Learning},
        duration={Aug 2022 -- March 2023},
        keyHighlight={Collaborated with a team to modify CNN models (VGG16, ResNet) for image classification.}
    ]
    \begin{itemize}
        \itemsep -6pt
        \item Modified and implemented multiple ML and neural network models to classify trimesters.  Applied machine learning models.
        \item Performed data augmentation, increasing dataset size by 30\%, leading to improved model accuracy.  Data analysis and optimization.
        \item Published findings in a research paper.
    \end{itemize}
    \projectItem[
        title={DLPM Data Lead Payable Management},
        duration={Feb 2024 -- Nov 2024},
        keyHighlight={Awarded Best Team Contributor for significant project contributions.}
    ]
    \begin{itemize}
        \itemsep -6pt
        \item Deployed an automated tool to classify invoices into PO and Non-PO categories.  Implementing automation solutions.
        \item Designed and implemented a machine learning model to achieve 95\% classification accuracy.  High performance machine learning.
        \item Automated invoice processing, reducing manual efforts and errors by 25\%. Enabled seamless ERP integration for streamlined data management.  Improving efficiency and reducing errors.
        \item Automated the extraction and converted invoice data into JSON format for structured storage in a database, enabling seamless integration with downstream processes and enhanced data accessibility.  Data structure and management.
        \item Enabled automated 2-way or 3-way matching for PO-based orders by integrating email-based invoice retrieval, reducing manual intervention and human errors.   Improving data quality.
        \item Optimized non-PO invoice workflows for enhanced accuracy and faster processing.  Optimization and efficiency improvements.
    \end{itemize}
\end{experienceSection}

\end{document}